Contracts for unions and intersections are hard for Nickel

### 2021-05-31 paper.tex
Small rewording conclusion

Alas, the implementation of union and intersection contracts is not as simple as
it first appears. In conjunction with higher-order contracts, or even just basic
contracts in a lazy language, they behave in a way that is reminiscent of
side-effects. These behaviors were, for most of them, already known: we do not
claim their discovery. However, as language implementers, we have made an actual
attempt at including them in a concrete language. We exposed what, in our
opinion, are the most salient flaws and their consequences. Even in a pure
language, union and intersection contracts break the equivalence between
call-by-name and call-by-value, and consequently can prevent CSE-like
optimizations. There are discrepancies between the expected and actual semantics
that make some behaviors unintuitive. Their implementation is a non-trivial
change that contaminates the evaluation of all other contracts, and the
performance penalty is not obvious to assess.

To conclude, let us make clear that we do not think union and intersection
contracts are fundamentally broken, that they can not be implemented correctly,
or that they do not bear any value (quite the contrary). They may still make
sense to have in a language, and some apparent difficulties in the
implementation could be lifted some day. But as often, there are gaps between
the theoretical framework, a proof-of-concept, a prototype, and the integration
in an actual language. We hope that our attempt may serve as a cautionary tale,
that for union and intersection contracts, these gaps are sometimes large in
places.

>>>>

Alas, the implementation of union and intersection contracts is not as simple as
it first appears. In conjunction with higher-order contracts, or even just basic
contracts in a lazy language, they behave in a way that is reminiscent of
side-effects. These behaviors were, for most of them, already known: we do not
claim their discovery. However, as language implementers, we have made an actual
attempt at including them in a concrete language. We exposed what, in our
opinion, are the most important barriers and their impact on the rest of the
language. Even in a pure setting, union and intersection contracts break the
equivalence between call-by-name and call-by-value, and can consequently prevent
optimizations. There are discrepancies between the expected and actual semantics
that make some behaviors unintuitive. Their implementation is a non-trivial
change that contaminates the evaluation of all other contracts, and the
performance penalty is not obvious to assess.

To conclude, let us make clear that we do not think union and intersection
contracts are fundamentally broken, that they can not be implemented correctly,
or that they do not bear any value (quite the contrary). They may still make
sense to have in a language, and some apparent difficulties in the
implementation could be lifted some day. But as often, there are gaps between
the theoretical foundation, a proof-of-concept, a prototype, and the integration
in an actual language. We hope that our attempt may serve as a cautionary tale:
for union and intersection contracts, these gaps might be quite large in places.
